Case Study: RNA-Seq Differential Analysis

### 2018-03-12 datasets/RNA-Seq/RNA-Seq.Rmd
Update RNA-seq analysis using smaller rds; uniform file names

---
title: "Case Study: RNA-Seq Differential Analysis"
author: "Chinmay Shukla"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

**Add brief summary of analysis goals and data set.**

@@

## set up parallel backend
cores <- as.numeric(Sys.getenv("SLURM_NTASKS"))
##multicoreParam <- MulticoreParam(workers = cores)
multicoreParam <- SerialParam()
```

@@

```{r, dsd-download}
dsd_data <- file.path(datdir, "dsdObjects.RData")
if (!file.exists(dsd_data)) {
    download.file("https://www.dropbox.com/s/8hf0ccl27ircodz/dsdObjects.RData?dl=1",
                  destfile = dsd_data)
}
load(dsd_data)
```

**Add details on content of data and subsetting.**

```{r}
## Filter to include samples from only 2 tissues
tissues <-  c('Brain - Nucleus accumbens (basal ganglia)',
              'Brain - Putamen (basal ganglia)')
filteredDsd1 <- dsd1[, colData(dsd1)$tissue %in% tissues]
filteredDsd1$tissue <- droplevels(filteredDsd1$tissue)
```

@@

```{r}
res_rda <- file.path(resdir, "dsd1-results.rda")
if (!file.exists(res_rda)) {
    ## build DESeq object and run DESeq2
    dds <- DESeq(filteredDsd1, parallel = TRUE, BPPARAM = multicoreParam)
    res <- results(dds, independentFiltering = FALSE)

    save(dds, res, file = res_rda)
} else {
    load(res_rda)
}
```

@@

```{r}
bd <- initializeBenchDesign()
sb <- buildBench(bd, data = geneExp, ftCols = "ind_covariate")
```

>>>>

---
title: "Case Study: RNA-Seq Differential Analysis"
author: "Chinmay Shukla, Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

**Add brief summary of analysis goals and details of data set.**
This data set includes 30 samples each from two regions of the human basal ganglia,
the nucleus accumbens and the putamen, obtained from the GTEx project.
Gene-level read counts were obtined by **fill**...

@@

## intermediary files we create below
count_file <- file.path(datdir, "brain-counts.rds")
result_file <- file.path(resdir, "brain-results.rds")
bench_file <- file.path(resdir, "brain-benchmark.rds")

## set up parallel backend
cores <- as.numeric(Sys.getenv("SLURM_NTASKS"))
multicoreParam <- SerialParam()
```

@@

The pre-computed set of samples can

```{r, dsd-download}
if (!file.exists(count_file)) {
    download.file("", destfile = count_file)
}
dsd <- readRDS(count_file)
```

@@

```{r}
if (!file.exists(result_file)) {
    ## build DESeq object and run DESeq2
    dds <- DESeq(dsd, parallel = TRUE, BPPARAM = multicoreParam)
    res <- results(dds, independentFiltering = FALSE)

    saveRDS(res, file = result_file)
} else {
    res <- readRDS(result_file)
}
```

@@

```{r}
if (!file.exists(bench_file)) {
    bd <- initializeBenchDesign()
    sb <- buildBench(bd, data = geneExp, ftCols = "ind_covariate")
    saveRDS(sb, file = bench_file)
} else {
    sb <- readRDS(bench_file)
}
```
